Supplementary 1 - Considering scale in multilayer animal social networks

### 2020-06-20 paper/supplement.Rmd
tidy
freq calc for lc

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # warning = FALSE,
    # message = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

# source('../scripts/00-variables.R')

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

@@

```{r}
data.table(freq(lc))[!is.na(value), count / sum(count)]

```
